\sf Retraction-based first-order feasible methods for difference-of-convex programs with smooth inequality and simple geometric constraints

### 2022-04-22 response_to_referee_v1.tex

\begin{table}[h]
\caption{Computational results for problem \eqref{pr1} with initial point $x^0$ is given as in (6.6)}\label{table3}
\begin{center}
{\footnotesize
\begin{tabular}{|c|c|c|c|c|c|c|}\hline
\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
\multirow{8}*{CPU time} & \multirow{1}*{QR}
&   0.56 &   3.17 &  10.04 &  23.39 &  45.84\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
&   0.01 &   0.02 &   0.06 &   0.10 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
&   3.24 &  13.12 &  34.00 & 205.99 & 233.59\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}
&   2.67 &  14.19 &  19.85 &  39.25 &  58.30\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{FPA$_{\rm retract}$}
&   4.57 & 191.87 &  40.39 & 128.89 & 160.03\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  17.38 &  66.68 & 123.05 & 211.69 & 179.34\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  16.54 &  65.41 & 137.92 & 217.52 & 294.88\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  18.35 &  82.69 & 195.55 & 329.15 & 397.47\\\cline{1-7} \multirow{5}*{Iter} & \multirow{1}*{SCP}
&    200 &    325 &    203 &    245 &    237\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{FPA$_{\rm retract}$}
&    577 &   6069 &    567 &   1072 &    859\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&   2590 &   2629 &   2204 &   2256 &   1236\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&   2479 &   2578 &   2470 &   2315 &   2026\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&   2766 &   3266 &   3505 &   3506 &   2741\\\cline{1-7} \multirow{6}*{RecErr} & \multirow{1}*{SPGL1}
&  1.699 &  3.423 &  1.826 &  2.630 &  2.465\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
&  0.071 &  0.073 &  0.075 &  0.074 &  0.075\\\cline{1-7} \multirow{6}*{Residual} & \multirow{1}*{SPGL1}
& -5.45e-01 & -5.84e-01 & -7.09e-01 & -7.08e-01 & -7.38e-01\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{SCP}
& -1.31e-10 & -1.53e-10 & -1.45e-10 & -1.78e-10 & -1.60e-10\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
& -1.25e-12 & -1.37e-12 & -1.18e-12 & -1.22e-12 & -1.07e-12\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
& 1.84e-11 & 1.94e-11 & 3.42e-11 & 4.38e-11 & 9.14e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
& 2.62e-11 & 2.35e-11 & 2.58e-11 & 2.87e-11 & 2.32e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
& 1.84e-11 & 1.52e-11 & 1.24e-11 & 1.41e-11 & 2.30e-11\\\cline{1-7}
\end{tabular}
}
\end{center}
\end{table}

From Table 3, one can see that the recovery errors of the algorithms are comparable, and SCP is usually faster. This is likely because SCP can take advantage of BB step size (and hence some sort of second-order information), but currently we still do not know how to take advantage of second-order information suitably in our scheme.

From the table above, it appears that our proposed method is not the method of choice when it comes to solving \eqref{pr1}.
Note that although the subproblems of SCP for \eqref{pr1} involve nonlinear constraints, thanks to the polyhedral nature of $\ell_1$ norm, they can still be solved efficiently via some root-finding procedure; see the appendix of [43]. This prompts us to consider some other objective functions where the corresponding SCP subproblems are not easy while the subproblems for our method (which are linearly constrained) can still be solved efficiently using Newton's method; this setting would be closer to our original motivation, as stated in footnote 1 of the manuscript.

One natural scenario arises from compressed sensing problems for complex signals with Cauchy noise, which results in the following problem that involves group-LASSO type objective. The derivation is detailed in the new Section 6.2.
\begin{equation}\label{E2}
  \begin{array}{rl}
    \min\limits_{x\in\R^n} & \sum\limits_{J\in\mathcal{J}}\|x_J\| - \mu\|x\| \\
    {\rm s.t.} & \|Ax - b\|_{LL_2,\gamma}\leq \overline{\sigma},
  \end{array}
\end{equation}
While theoretically one can apply SCP to the above problem, it is unclear to us how the subproblems, which are nonlinearly constrained, can be solved efficiently. In contrast, the subproblems that arise in our approach can still be solved efficiently using Newton's method. We have now adopted this complex version of compressed sensing problems in our numerical experiment section. 
%Notice that this problem can not be solved efficiently by SCP in [42] (as we don't know how to efficiently solve the subproblem of SCP in this case). Hence we replace problem (6.3) in article with problem \eqref{E2}, and have modified it accordingly. We compare FPA$_{\rm retract}$ and ESQM$_{\rm ls}$ on solving random instances of \eqref{E2}. The results are shown in Table 4 and Table 5, which correspond to different initial points.
%
%\begin{table}[H]
%\caption{Computational results for problem \eqref{E2} with initial point $x^0$ is given as in (6.6)}\label{table3}
%\begin{center}
%{\footnotesize
%\begin{tabular}{|c|c|c|c|c|c|c|}\hline
%\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
%& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
%\multirow{7}*{CPU time} & \multirow{1}*{QR}
%&   0.63 &   4.27 &  11.15 &  24.66 &  51.66\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
%&   0.01 &   0.03 &   0.05 &   0.10 &   0.15\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
%&   1.18 &  11.16 &  34.97 &  43.14 &  95.33\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&   3.64 &  15.43 &  34.70 &  46.92 &  88.78\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  13.62 &  34.03 &  41.46 &  59.36 &  57.94\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  15.86 &  47.38 &  57.92 &  80.34 & 132.93\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  17.33 &  59.84 & 111.44 & 181.45 & 208.90\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
%&    224 &    363 &    410 &    340 &    424\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&   1423 &   1125 &    670 &    570 &    366\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&   1655 &   1563 &    939 &    787 &    866\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&   1820 &   2001 &   1841 &   1832 &   1365\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
%&  0.867 &  1.490 &  1.806 &  1.360 &  1.768\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
%& -5.23e-01 & -6.27e-01 & -6.81e-01 & -6.56e-01 & -7.32e-01\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%& -2.88e-12 & -2.41e-12 & -2.42e-12 & -2.41e-12 & -2.17e-12\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%& 3.88e-11 & 6.21e-11 & 1.42e-10 & 1.16e-10 & 2.90e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%& 4.15e-11 & 6.45e-11 & 1.26e-10 & 6.73e-11 & 6.65e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%& 3.11e-11 & 2.71e-11 & 3.73e-11 & 4.77e-11 & 7.86e-11\\\cline{1-7}
%\end{tabular}
%}
%\end{center}
%\end{table}
%
%
%
%\begin{table}[H]
%\caption{Computational results for problem \eqref{E2} with initial point $x^0= (0, 0, \cdots, 0)$}\label{table3}
%\begin{center}
%{\footnotesize
%\begin{tabular}{|c|c|c|c|c|c|c|}\hline
%\phantom{\diagbox{Date}{$i$}} & \multicolumn{1}{|c|}{Method} & \multicolumn{1}{|c|}{$i = 2$} & \multicolumn{1}{c|}{ $i = 4$ }
%& \multicolumn{1}{c|}{ $i = 6$ } & \multicolumn{1}{|c|}{ $i = 8$ } & \multicolumn{1}{c|}{ $i = 10$ }\\\cline{1-7}
%\multirow{7}*{CPU time} & \multirow{1}*{QR}
%&   0.61 &   4.14 &  10.99 &  40.10 &  58.79\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{Slater}
%&   0.01 &   0.03 &   0.05 &   0.15 &   0.16\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{SPGL1}
%&   1.15 &  11.15 &  34.89 & 757.10 &  95.79\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&   5.05 &  19.66 &  41.70 &  69.97 &  98.92\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  13.02 &  35.24 &  51.35 &  92.84 &  76.91\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  15.68 &  46.91 &  64.06 & 123.14 & 152.65\\\cline{2-2} \multirow{1}*{}  & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  19.24 &  64.05 & 122.80 & 238.13 & 231.80\\\cline{1-7} \multirow{4}*{Iter} & \multirow{1}*{FPA$_{\rm retract}$}
%&    320 &    440 &    496 &    381 &    469\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&   1353 &   1152 &    836 &    672 &    487\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&   1652 &   1555 &   1045 &    989 &    984\\\cline{2-2} \multirow{1}*{}     & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&   2055 &   2112 &   2048 &   1942 &   1498\\\cline{1-7} \multirow{5}*{RecErr} & \multirow{1}*{SPGL1}
%&  0.867 &  1.490 &  1.806 &  1.360 &  1.768\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%&  0.048 &  0.051 &  0.052 &  0.052 &  0.052\\\cline{1-7} \multirow{5}*{Residual} & \multirow{1}*{SPGL1}
%& -5.23e-01 & -6.27e-01 & -6.81e-01 & -6.56e-01 & -7.32e-01\\\cline{2-7} \multirow{1}*{} & \multirow{1}*{FPA$_{\rm retract}$}
%& -2.82e-12 & -2.47e-12 & -2.45e-12 & -2.52e-12 & -2.20e-12\\\cline{2-2} \multirow{1}*{} & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.5}$}
%& 6.59e-11 & 4.79e-11 & 2.57e-10 & 1.05e-10 & 2.68e-10\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.1}$}
%& 5.94e-11 & 6.38e-11 & 8.28e-11 & 8.97e-11 & 9.09e-11\\\cline{2-2} \multirow{1}*{}      & \multirow{1}*{ESQM$_{{\rm ls},\ \delta = 0.02}$}
%& 3.14e-11 & 3.01e-11 & 3.56e-11 & 4.44e-11 & 8.38e-11\\\cline{1-7}
%\end{tabular}
%}
%\end{center}
%\end{table}
